\mythesistitleNOTSYNPOSIS \tnote{Synopsis title is ``Generalization of Consecutive Ones Property of Binary Matrices''}

### 2012-01-14 src/020chap2.tex
Started cleaning up chapter 3. Deferring it though to work on Chapter 2. Need to accommodate N's new proofs for removal of algorithmic charac.
See diff for other changes left out in this comment.

@@

   \begin{tabular}[h]{lll}
     \hline
     \hline
     % 
     1899 & \parbox[t]{\tabparboxw}{ First mention of \COP
       (archaeology)} & \parbox[t]{2cm}{\temptext{by petrie -- cite
         kendall 69 pacific journal of mathematics 1969 }}  \\

@@

A few years later, a deeply significant result based on very
different ideas in understanding \COP came from Tucker which gave a
combinatorial (negative) characterization of matrices with COP
\cite{at72}. This result influenced most of the \COP results that
followed in the literature \annote[pressing]{including linear time
  algorithms}{did it? which ones?} for \COP recognition.

@@

\begin{definition}[\emph{\PQtree \cite{bl76, mcc04}}]\\
  A \PQtree of matrix $M$ with \COP on columns (rows), is a tree with the following properties.
  \begin{enumerate}[i.]
    \singlespacing
  \item Each leaf uniquely represents a row (column) of $M$. The leaf
    order of the tree gives a \COP order for column (row)\endnote{Note
      that \COP order for column requires permutation of rows and vice
      versa.} for $M$.
  \item Every non-leaf node in the tree is labeled $P$ or $Q$.
  \item \label{def::nodep} The children of $P$ nodes are
    unordered. They can be permuted in any fashion to obtain a new
    \COP order for $M$.
  \item \label{def::nodeq} The children of $Q$ nodes are linearly
    ordered. Their order can be reversed to obtain a new \COP
    order for $M$.
  \end{enumerate}
  \label{def:pqtree}
\end{definition}

@@

Any set system that is closed under the above operations and contains
$\cT(U)$ is called {\complete} \cite{mm96} or a {\em weakly partative
  family} \cite{mcc04}. Such a set system is easier to
work with for reasons that will become apparent.\tnote{VAGUe!}
For any set system $\cF$, the smallest super set system that is
complete/weakly partative is called the {\em weak closure} of $\cF$,
denoted $\cW(\cF)$ \cite[Def.~3.2]{mcc04}. \cite[Def.~2, smallest {\em
  complete} supercollection]{mm96}.

>>>>

    \tnote[important]{1899 by petrie -- cite
         kendall 69 pacific journal of mathematics 1969 }

@@

  \begin{tabular}{lll}
     \hline
     \hline
     % 
     1899 & \parbox[t]{\tabparboxw}{ First mention of \COP
       (archaeology)} & 
       \\ % \parbox[t]{2cm}{}

@@

A few years later, a deeply significant result based on very different
ideas in understanding \COP came from Tucker which gave a
combinatorial (negative) characterization of matrices with COP
\cite{at72}. This result influenced most of the \COP results that
followed in the literature including linear time
algorithms\tnote[pressing]{linear? did it? which ones?} for \COP
recognition.

@@

\begin{definition}[\PQtree \cite{bl76, mcc04}]
  A \PQtree of matrix $M$ with \COP on columns (rows), is a tree with the following properties.
  \begin{enumerate}[i.]
    \singlespacing
  \item Each leaf uniquely represents a row (column) of $M$. The leaf
    order of the tree gives a \COP order for column (row)\endnote{Note
      that \COP order for column requires permutation of rows and vice
      versa.} for $M$.
  \item Every non-leaf node in the tree is labeled $P$ or $Q$.
  \item \label{def::nodep} The children of $P$ nodes are
    unordered. They can be permuted in any fashion to obtain a new
    \COP order for $M$.
  \item \label{def::nodeq} The children of $Q$ nodes are linearly
    ordered. Their order can be reversed to obtain a new \COP
    order for $M$.
  \end{enumerate}
  \label{def:pqtree}
\end{definition}

@@

Any set system that is closed under the above operations and contains
$\cT(U)$ is called {\em complete} \cite{mm96} or a {\em weakly partative
  family} \cite{mcc04}. Such a set system is easier to
work with for reasons that will become apparent.\tnote{VAGUe!}
For any set system $\cF$, the smallest super set system that is
complete/weakly partative is called the {\em weak closure} of $\cF$,
denoted $\cW(\cF)$ \cite[Def.~3.2]{mcc04}. \cite[Def.~2, smallest {\em
  complete} supercollection]{mm96}.
